Fig1

### 2020-08-06 analysis/figure-1.Rmd
better fig 1

```{r tSNE-df, fig.width=7, fig.height=5.25}
# prep for tsne useing count data from limma and the custom `subsetmaketsne` function
hyptsne <- subsetmaketsne("hypothalamus", alllevels, sexlevels)
pittsne <- subsetmaketsne("pituitary", alllevels, sexlevels)
gontsne <- subsetmaketsne("gonads", alllevels, sexlevels)
```

@@

```{r fig1, fig.width=7, fig.height=5.5}

@@

e1 <- plottsneelipsev3(hyptsne, hyptsne$treatment, allcolors) + 
  labs(subtitle = "hypothalamus") 
e2 <- plottsneelipsev3(pittsne, pittsne$treatment, allcolors ) + 
  labs(subtitle = "pituitary") 
  theme(strip.text = element_blank())
e3 <- plottsneelipsev3(gontsne, gontsne$treatment, allcolors ) + 
  labs(subtitle = "gonads", caption = "Perplexity = 50")

e <- plot_grid(e1,e2,e3, ncol = 3, labels = c("E"), label_size = 8)

fig1 <- plot_grid(a, e, nrow = 2, rel_heights = c(2.5,2))
fig1
```

@@

```{r write}
# save file for musical genes https://raynamharris.shinyapps.io/musicalgenes/
#write.csv(allDEG, "../../musicalgenes/data/allDEG.csv")

# tsne files too big to save
#write.csv(chartsne, "../../musicalgenes/data/tsne.csv")

pdf(file="../figures/fig1-1.pdf", width=7.25, height=7.25)
plot(fig1)
dev.off()
```

>>>>

```{r tSNE-df}
# prep for tsne useing count data from limma and the custom `subsetmaketsne` function
hyptsne <- subsetmaketsne("hypothalamus", alllevels, sexlevels)
pittsne <- subsetmaketsne("pituitary", alllevels, sexlevels)
gontsne <- subsetmaketsne("gonads", alllevels, sexlevels)
```

@@

```{r fig1, fig.width=7, fig.height=4.5}

@@

e1 <- plottsneelipsev3(hyptsne, hyptsne$treatment, allcolors) + 
  labs(subtitle = "hypothalamus") 
e2 <- plottsneelipsev3(pittsne, pittsne$treatment, allcolors ) + 
  labs(subtitle = "pituitary") 
  theme(strip.text = element_blank())
e3 <- plottsneelipsev3(gontsne, gontsne$treatment, allcolors ) + 
  labs(subtitle = "gonads")

e <- plot_grid(e1,e2,e3, ncol = 3, labels = c("D"), label_size = 8)

fig1 <- plot_grid(a, e, nrow = 2, rel_heights = c(2.4,1.6))
fig1
```

@@

```{r write}
pdf(file="../figures/fig1-1.pdf", width=7, height=4.5)
plot(fig1)
dev.off()
```
